Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-09-23 docs/manuscript/manuscript.tex
Updates from Overleaf

\begin{itemize}
    \item Attempting reproductions
    \item Attempting reproductions in geography
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Prior Survey Research on Reproducible Research}
\begin{itemize}
    \item Reproducibility surveys
    \item the problems with these surveys
    \item reproducibilty surveys in geography
    \item how they fall prey to the same problems
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Assessing the Reproducibility of Research}
The reproducibility of research can be assessed directly or indirectly \citep{NASEM2019}.

In a direct assessment of reproducibility 
Indirect reproducibility assessments

There are several ways to assess the reproducibility of research.
The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study.

\subsection*{Direct Reproducibility Assessments}
Direct reproducibility assessments can be implemented in two ways: as a one-to-one comparison, in which a single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple parallel reproductions and make a set of comparisons and a collective assessment of one prior study.
Published reproductions of both forms are becoming increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
However, the researchers conducting those studies have generally only able to partially reproduce study results, often observing small effect sizes.

Such published reproductions have not yet become common in geography. 
The small number of studies that have attempted to assess the reproducibility of geographic research by recreating existing work suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort. 
A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} similarly identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
\citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).

Moving past the question of whether the computational results of a study can be recreated using the same data and code, a handful of geographic researchers are using the reproduction process as a way of examining not only the execution of a prior study, but its conceptualization and inferences \citep{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP}. 
While this form of the direct approach to reproduction opens a new door to the critical evaluation of geographic research, it primarily provides evidence about a particular research study and the phenomenon that study investigates. 
Similarly, while computationally focused reproductions have produced useful guidelines \citep{hofer2019reproducible, wilson2021} and moved forward the development of the computational and institutional infrastructure \citep{Kedron_Holler_Bardin_Hilgendorf_2022, nust2019, nust2021,}\textbf{ADD SHAOWEN} needed to foster reproducibility in the field, they have not yet assessed the use of reproducible research practices across the disciplines diverse research traditions, or identified the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.

The root of the problem is that the direct approach to assessing reproducibility presents a trade off. 
The careful reproduction of a study can provide rich evidence about that particular study, but offers at best suggestive evidence about the validity of other studies or the prevalence of the research practices observed.
For example, if a reproduction identified a flaw in the design of a study that impacted the results of that study it would be reasonable to be concerned that observing the same flaw in other studies could impact the results of those studies.
However, until other studies are gathered and checked we would not know how common the flaw is, or if it impacts other studies in a similar way.

\subsection*{Indirect Reproducibility Assessments}
Indirect reproducibility assessments are one way to address this breadth problem. 
During  the indirect approach to reproducibility assessment a researcher gathers information about the transparency and availability of information needed to attempt reproduction and the

An alternative approach to understanding the reproducibility of research is to survey active researchers about their perceptions of reproducibility and their own research practices.
Researcher surveys measure reproducibility indirectly by gathering information about research transparency and researcher practices and motivationsthat

can be used to understand how common certain practices are and what motivates those practices.

Surveys of researchers working across the sciences suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
Perceptions on the cause of irreproducibility range from natural variation to fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}, with an estimated 33 percent of researchers admitting to some form of questionable research practices \citep{fanelli2009many}.  
Researchers also appear to support a broad range of solutions to the challenge of irreproducibility including improved training in research design and statistics and better research mentoring and supervision \citep{baker20161}.

\subsubsection{Geog Indirect}
To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
In a survey of participants from the 2016 European Geosciences Union General Assembly, \citet{konkol2019} assessed the frequency with which researchers published their work in ways that enabled computational reproducibility. 
Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.

\subsubsection{common problems of surveys}
While these surveys are suggestive of reproducibility concerns across the sciences, they share a set of common methodological problems. 
First, many prior surveys have used non-systematic sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships), and/or use non-probability sampling schemes, which collectively limits our ability to draw generalizable conclusion or make inferences about specific sub-fields \citep{NASEM2019}.
Prior surveys also commonly failed to systematically report survey details (e.g., response rate) needed to assess and address potential bias. 
To make sound conclusions about the extent of irreproducibility in geography, we need to not only gather additional evidence, we need to do so in a manner consistent with the best practices for survey research \citep[see][]{dillman2014internet, aapor}.
